\documentclass[11pt]{report}

\special{papersize=8.5in,11in}

\topmargin -0.5in \oddsidemargin 0.00in \evensidemargin 0.00in
\textwidth 6.75in \textheight 9.0in \headheight 0.25in \headsep
0.25in \footskip 0.5in \hoffset 0in \marginparpush 0.0in
\marginparwidth 0.0in \marginparsep 0.2in

\setcounter{page}{1}

\newcommand{\D}{\displaystyle}\newcommand{\T}{\textstyle}
\newcommand{\e}{{\mathrm{exp}}}
\newcommand{\dd}{{\mathrm d}}
\newcommand{\comment}[1]{}
\reversemarginpar

\usepackage[final]{graphicx}
\usepackage{fancyhdr}
%\graphicspath{{Papers/}}
\usepackage{amsthm,amssymb,amsmath}

\title{Guidelines to Prepare a Research Progress Report}

\author{Prof. H. H. Nguyen}

\begin{document}

\maketitle

\lhead{\sf Guidelines to Prepare a Research Progress Report} \chead{} \rhead{\sf Prof. H. Nguyen}
\lfoot{CTRG, University of Saskatchewan} \cfoot{} \rfoot{Page \thepage}
\renewcommand{\footrulewidth}{1.0pt}
\renewcommand{\headrulewidth}{2.0pt}
\pagestyle{fancy}

\renewcommand{\thesection}{\arabic{section}}

\chapter{Weeks of October 1 and 8, 2007}

\section*{Introduction}

This template provides guidelines on how to prepare/organize your research progress biweekly. Feel free to include figures, tables, etc. as needed. Please also document and organize your bibliography file similarly to the attached sample bib file. A citing example is as follows: \cite{Nguyen0705,Alouini-TCOM-03-2000}.

As indicated, report is required every two weeks, on Monday (Saskatoon time) of the due week, at any time and via email (\verb"ha.nguyen@usask.ca"). The following are the \textbf{first} due dates applied to you:

\begin{itemize}
\item Duy Nguyen: October 12
\item Tung Pham:  October 12
\item Nam Vien:  October 12

\item Zohreh Andalibi:  October 19
\item Ha Xuan Nguyen:  October 19
\item Son Hoang:  October 19
\end{itemize}

Of course you can send me your updated progress report any time if you think my early feedback might be useful. However, I might not be able to response right away.

Preparing the report in \LaTeX\; is required. Always use the same \LaTeX\; file. You just simply add more content to it as a new chapter. I will provide my comments into the \LaTeX\; file as well. The following are suggested sections in each report (chapter):

\section{Summary of Reading and Research Activities}

\section{Accomplishments}

\section{Objectives for the Next 2 Weeks}

\section{Advisor's Comments}

%\bibliographystyle{IEEEtran}
\bibliographystyle{ieeetr}

\bibliography{Sample_BIB_File}

\end{document}